Stack Safety as a Security Property

### 2020-06-05 main.tex
CP

\leo{I hate the writing here, but I wanted to make a start.}  The call
stack is an increasingly popular target for attacks exploiting memory
safety vulnerabilities, with potential consequences ranging from
attackers reading or corrupting private stack data, to highjacking a
programs control flow. To prevent such attacks, many techniques have
been proposed in the literature\leo{cite, point out? stack canaries,
  cherry, nicks...} aiming to achieve {\em stack safety}.

But what does stack safety even mean? A formal definition of stack
safety is missing from the literature, with the notion only being
defined negatively: through examples of stack unsafety. Two classical
examples of stack unsafety appear in Figure~\ref{fig:stackunsafety}.
\leo{Goal: on the left, a bad read; on the right, a bad right.}

@@

While integrity and confidentiality are relatively standard security
properties, this setting provides an interesting additional challenge:
the notion of who the attacker shifts throught execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be potentially proteced from {\em its} callees.

Roadmap: 
Preliminaries before all these.

Contributions:
\begin{itemize}
\item A formal property capturing the informal understanding of what ``stack safety'' is.
\item Evidence that this property is strong enough to capture the folk
intuition: we show that the stack
  unsafe examples from the literature also fail our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism \leo{And it
    says yes on a substantial body of code}
\item A (inductive? step-by-step/stepwise) variant of this property
  tuned for testing/verification together with a proof that it implies
  the original property.  We test the whole thing with a cool
  framework.
\item A lazy version of the property that allows for more efficient/dynamic enforcement.
  Maybe testing.
\item TODO: Logic? Reasoning Principles?
\end{itemize}

Related work pointer + conclusions.

\section{Background}

@@

\section{Future Work}

>>>>

\leo{I hate the writing here, but I wanted to make a start.}

The call stack is an increasingly popular target for attacks
exploiting memory safety vulnerabilities, with potential consequences
ranging from attackers reading or corrupting private stack data, to
highjacking a program's control flow. To prevent such attacks, many
techniques have been proposed in the literature\leo{cite, point out?
  stack canaries, cherry, nicks...} aiming to achieve {\em stack
  safety}.

But what {\em is} stack safety? A formal definition of stack safety is
lacking from the literature, with the notion only being defined
negatively: through examples of stack unsafety. Two classical examples
of stack unsafety appear in Figure~\ref{fig:stackunsafety}.
\leo{Goal: on the left, a bad read; on the right, a bad write.}

@@

While integrity and confidentiality are relatively standard security
properties, this setting provides an interesting additional challenge:
the notion of who the attacker shifts throught execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be potentially proteced from {\em its} callees.  In
this paper we address this challenge by varying the observation power
of the attacker at call points, and demonstrate that our policy is
implementable by pre-existing monitoring mechanisms.

We begin by giving some background in Section~\ref{sec:prelim}.
Our contributions are:
\begin{itemize}
\item A formal property capturing the informal understanding of what ``stack safety'' is.
\item Evidence that this property is strong enough to capture the folk
intuition: we show that the stack
  unsafe examples from the literature also fail our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism \leo{And it
    says yes on a substantial body of code}
\item A (inductive? step-by-step/stepwise) variant of this property
  tuned for testing/verification together with a proof that it implies
  the original property.  We test the whole thing with a cool
  framework.
\item A lazy version of the property that allows for more efficient/dynamic enforcement.
  Maybe testing.
\end{itemize}
Finally, in Section~\ref{sec:relwork} we discuss related work and
sketch directions for future work in Section~\ref{sec:future}.

\section{Background}
\label{sec:prelim}

@@

\section{Related Work}
\label{sec:relwork}

\section{Future Work}
\label{sec:future}
